Proportional multi-state multiple-cohort life table model

### 2018-04-10 MSLT/MSLTdoc.Rmd
Added females graphs
Next, do a loop for all measures (deaths, prevalenc,e, incidence, prevalence, ylds)

##Plot all cause mortality rates males 
mx_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
    geom_line(aes(color = "England"))+
    geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
    labs(colour="Locations",x="Age",y="Mortality rate")+
    theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
    scale_color_manual(values = c("blue","red"))+
    theme_classic()

@@

>>>>

##Plot all cause mortality rates males 
mx_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
    geom_line(aes(color = "England"))+
    geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
    labs(colour="Locations",x="Age",y="Mortality rate")+
    theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
    scale_color_manual(values = c("blue","red")) +
    labs (title = "Mortality rates difference males") +
    theme_classic()

@@

##Select data from data frames for all cause mortality females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause mortality rates males 
mx_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
    geom_line(aes(color = "England"))+
    geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
    labs(colour="Locations",x="Age",y="Mortality rate")+
    theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
    scale_color_manual(values = c("blue","red")) +
    labs (title = "Mortality rates difference females") +
    theme_classic()

print(mx_plot_compare_female)
